### 2012-12-15 inst/examples/reed-example.Rmd
Underlying BH model compared to estimated GP and Ricker.

```{r set-options, echo = FALSE, cache = FALSE, external = TRUE}
opts_chunk$set(external = TRUE, cache = TRUE, cache.path = "bevholt-cache/")
read_chunk('gaussian-process-control.R')
library(knitcitations)
```

@@

We use the model of `r citet("10.1126/science.269.5227.1106")`.

@@

>>>>

```{r set-options, echo = FALSE, cache = FALSE, external = TRUE}
opts_chunk$set(external = TRUE, cache = FALSE, cache.path = "bevholt-cache/")
read_chunk('gaussian-process-control.R')
library(knitcitations)
```

@@

We use the model of

@@

Estimates a Ricker curve with parameters $r =$ `r p_alt[1]` and $K =$ `r p_alt[2]`
